Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints

### 2017-11-06 2017/ParOptBook/Chapter4.tex
Chapter 2 included

\section*{A brief conclusion}
Constrained global optimization problems are under consideration. The method of penalty functions is one of the most popular numerical methods for solving the problems of this kind. Nevertheless, the method of penalty functions has a number of disadvantages. A new method for reduction of a constrained problem to an unconstrained one, so called \emph{index method}, has been considered in this chapter. This method, unlike the classical penalty function one, allows avoiding the problem of the parameter selection (like the penalty coefficients for the constraints). It is also allows solving the problems with partially defined objective function and constraints. This is quite natural for many applied problems, especially, in the optimal design of technical systems, because if some conditions of operation are not met, then some other characteristics of the system performance may not be defined.

The issues of convergence acceleration of the index method have been considered also. Two approaches for the convergence acceleration have been proposed. The first of them is based on concept of $\varepsilon$-reserved solution to the constrained problem. The role of $\varepsilon$-reserved solution in constrained global optimization problems is somewhat similar to the regularity requirements in classical nonlinear programming problems. The second approach is based on adaptive order of checking for constraints. In the index method, every iteration performed at the corresponding point of the search domain includes checking for constraints of the problem at this point. When a violation is discovered for the first time, the current iteration is stopped, and the next iteration is initiated. However, in Lipschitz optimization problems a constraint violated at a point of the search domain is also violated in a certain neighborhood of this point. In this case, to reduce the number of checks, it is expedient to begin iterations in the neighborhood of this point with checking for the violated constraint. Thus, the iteration can be completed at a lower cost.

For all proposed algorithms, the results of numerical experiments are presented. The results confirm the theoretical statements about convergence acceleration.
\begin{thebibliography}{99.}
  \bibitem{stronginMarkin1986} Strongin, R.G., Markin, D.L.: Minimization of multiextremal functions under nonconvex constraints. Cybernetics \textbf{22}(4), 486---493 (1986)
  \bibitem{stronginMarkin1987} Markin, D. L., Strongin, R. G.: A Method for Solving Multi-Extremal Problems with Non-Convex Constraints, That Uses a Priori Information about Estimates of the Optimum. Comput. Maths. Math. Phys. \textbf{27}(1), 33---39 (1987)
  \bibitem{strongin1992} Strongin, R.G.: Algorithms for multi-extremal mathematical programming problems employing the set of joint space-filling curves. Journal of Global Optimization \textbf{2}(4), 357--378 (1992)
  \bibitem{stronginSergeyev2000} Strongin, R.G., Sergeyev, Y.D.: AGlobal Optimization with Non-Convex Constraints. Sequential and Parallel Algorithms. Kluwer Academic Publishers, Dordrecht (2000)
  \bibitem{SergeyevFamularoPugliese2001} Sergeyev Ya.D., Famularo D., Pugliese P.: Index Branch-and-Bound Algorithm for Lipschitz univariate global optimization with multiextremal constraints. Journal of Global Optimization \textbf{21}(3), 317---341 (2001)
  \bibitem{barkalovStrongin2002} Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of checking for constraints. Comput. Maths. Math. Phys. \textbf{42}(9), 1289---1300 (2002)
  \bibitem{SergeyevFamularoPugliese2003} Sergeyev Ya.D., Pugliese P., Famularo D.: Index information algorithm with local tuning for solving multidimensional global optimization problems with multiextremal constraints. Mathematical Programming \textbf{96}(3), 489---512. (2003)
  \bibitem{sergeyev2006} Sergeyev Ya.D.: Univariate global optimization with multiextremal non-differentiable constraints without penalty functions. Computational Optimization and Applications \textbf{34}(2), 229---248 (2006)
  \bibitem{sergeyevKhalafKvasov2007} Sergeyev, Y.D., Khalaf, F.M.H., Kvasov, D.E.: Univariate algorithms for solving global optimization problems with multiextremal non-differentiable constraints. In: A. T\"orn, J. ä ilinskas (eds.) Models and Algorithms for Global Optimization, Springer, 123---140 (2007)
  \bibitem{sergeyevKvasovKhalaf2007} Sergeyev Ya.D., Kvasov D.E., Khalaf F.M.H.: A one-dimensional local tuning algorithm for solving GO problems with partially defined constraints. Optimization Letters \textbf{1}(1), 85---99 (2007)
\end{thebibliography}
%\end{document}

>>>>

\begin{thebibliography}{99.}
  \bibitem{stronginMarkin1986} Strongin, R.G., Markin, D.L.: Minimization of multiextremal functions under nonconvex constraints. Cybernetics \textbf{22}(4), 486---493 (1986)
  \bibitem{stronginMarkin1987} Markin, D. L., Strongin, R. G.: A Method for Solving Multi-Extremal Problems with Non-Convex Constraints, That Uses a Priori Information about Estimates of the Optimum. Comput. Maths. Math. Phys. \textbf{27}(1), 33---39 (1987)
  \bibitem{strongin1992} Strongin, R.G.: Algorithms for multi-extremal mathematical programming problems employing the set of joint space-filling curves. Journal of Global Optimization \textbf{2}(4), 357--378 (1992)
  \bibitem{stronginSergeyev2000} Strongin, R.G., Sergeyev, Y.D.: AGlobal Optimization with Non-Convex Constraints. Sequential and Parallel Algorithms. Kluwer Academic Publishers, Dordrecht (2000)
  \bibitem{SergeyevFamularoPugliese2001} Sergeyev Ya.D., Famularo D., Pugliese P.: Index Branch-and-Bound Algorithm for Lipschitz univariate global optimization with multiextremal constraints. Journal of Global Optimization \textbf{21}(3), 317---341 (2001)
  \bibitem{barkalovStrongin2002} Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of checking for constraints. Comput. Maths. Math. Phys. \textbf{42}(9), 1289---1300 (2002)
  \bibitem{SergeyevFamularoPugliese2003} Sergeyev Ya.D., Pugliese P., Famularo D.: Index information algorithm with local tuning for solving multidimensional global optimization problems with multiextremal constraints. Mathematical Programming \textbf{96}(3), 489---512. (2003)
  \bibitem{sergeyev2006} Sergeyev Ya.D.: Univariate global optimization with multiextremal non-differentiable constraints without penalty functions. Computational Optimization and Applications \textbf{34}(2), 229---248 (2006)
  \bibitem{sergeyevKhalafKvasov2007} Sergeyev, Y.D., Khalaf, F.M.H., Kvasov, D.E.: Univariate algorithms for solving global optimization problems with multiextremal non-differentiable constraints. In: A. T\"orn, J. ä ilinskas (eds.) Models and Algorithms for Global Optimization, Springer, 123---140 (2007)
  \bibitem{sergeyevKvasovKhalaf2007} Sergeyev Ya.D., Kvasov D.E., Khalaf F.M.H.: A one-dimensional local tuning algorithm for solving GO problems with partially defined constraints. Optimization Letters \textbf{1}(1), 85---99 (2007)
\end{thebibliography}
%\end{document}
